Clustering in a hyperbolic model of complex networks.

### 2019-02-05 clustering_infinite_model.tex
updated notation and added comments to sections 1-3

\section{Clustering in $G_{\mathcal{P}}(\alpha, \nu)$}\label{sec:asymptotics_average_clustering_ast_P}

In this section we will establish the exact expressions for the limit local clustering coefficient and function, $c_\Pcal$ and $c_{\Pcal}(k)$, respectively. This is done in several steps. Recall that for $p\in \R \times \R_+ := \Rcal$,
\[
	\BallPo{p} = \{p^\prime \in \R \times \R_+ : |x - x^\prime| \le e^{\frac{y + y^\prime}{2}}\},
\]
denotes the neighborhood ball of $p$. Furthermore we recall the definition of $\Delta_\Pcal$ 
\[
	\Delta_{\Pcal}(y) = \iint_{\Rcal^2} T_\Pcal(p,p_1,p_2) \eta_{y}(x_1,y_1)\eta_{y}(x_2,y_2) \, dx1 \, dx_2 \, dy_1 \, dy_2,
\]
where $\eta_{y} = \frac{\mu_{\alpha,\nu}|_{\BallPo{(0,y)}}}{\Mu{\BallPo{(0,y)}}}$ is the marginal probability density associated with a randomly sampled neighbor of $(0,y)$.

We already noted that $\Delta_\Pcal(y)$ denotes the probability that two randomly sampled neighbors of $(0,y)$ are connected. More precisely, let $Z_{1}, Z_{2}$ be two independent random variables on $\BallPo{(0,y)}$, with (marginal) probability measures $\eta_{y}$. Then
\begin{equation}\label{eq:def_delta_p_alt}
	\Delta_{\Pcal}(p) = \pr_{\Pcal,p}\left( Z_{1} \in \mathcal{B}_{\Pcal}(Z_{2})\right)
\end{equation}
where $\pr_{\Pcal,p}$ denotes the joint probability measure of $Z_1$ and $Z_2$. We shall often abuse notation and write $\Delta_\Pcal(y)$ to denote $\Delta_\Pcal((0,y))$.

%Next we note that conditioned on the Poisson process $\Pcal$ having $k$ points in $\mathcal{B}_{\Pcal}(p)$, the points are independent random variables $Z_{1}, \dots, Z_{k}$, each with probability measure $\eta_{p}$ and hence
%\[
%	\Delta_{\Pcal}(p,k) = \binom{k}{2} \Delta_\Pcal(p).
%\]
%
%In addition, since $\mu_{\alpha, \nu}(B_\Pcal(p)) = \xi_{\alpha,\nu} e^{\frac{y}{2}}$, with $\xi_{\alpha,\nu} = \frac{4\alpha\nu}{(2\alpha - 1)\pi}$, and
%\[
%	\Delta_{\Pcal}(p) = \iint_{\Rcal^2} T_\Pcal(p,p_1,p_2) \eta_{p}(x_1,y_1)\eta_{p}(x_2,y_2) \, dx1 \, dx_2 \, dy_1 \, dy_2,
%\]
%we have that
%\begin{equation}\label{eq:relation_T_vs_Delta_P}
%	\Exp{T_\Pcal(p)} = \xi_{\alpha,\nu}^2 \frac{e^{y}}{2} \Delta_\Pcal(p).
%\end{equation}

We will start with some preliminary results on the degrees in $G_\Pcal(\alpha, \nu)$. The proof of Theorem \ref{thm:asymptotics_average_clustering_P} can be found in Section \ref{ssec:asymptotics_local_clustering_P}. The key ingredient for the proof is a result concerning the asymptotic behavior of $\Delta_\Pcal(y)$ (Proposition \ref{prop:asymptotics_Delta_y_P}) whose proof can be found in Section \ref{ssec:asymptotics_Delta_y_P}. The final computations for the exact expressions of $c_\infty$ in Theorem~\ref{thm:clustering_coefficient_hyperbolic} and $c_\infty(k)$ in Theorem~\ref{thm:local_clustering_hyperbolic} can be found in Section~\ref{ssec:exact_expressions_clustering_P}.

\subsection{Degree distribution in $G_\Pcal(\alpha, \nu)$}

Before we analyze local clustering in the infinite limit model, we first establish some results for its degree distribution. We define the probability distribution for the degree of node $p = (x,y)$ as
\begin{equation}
	\rho(p,k) = \Prob{D_\Pcal(p) = k} = \Prob{\Po(\mu_{\alpha,\nu}(\BallPo{p})) = k},
\end{equation}
where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$. Recall from equation \eqref{eq:mu_ball_y_P} that
\[
	\mu_{\alpha,\nu}(\BallPo{p}) = \xi_{\alpha,\nu} e^{\frac{y}{2}},
\]
only depends on the $y$-coordinate of $p$. Therefore, we will often write $\rho(y,k)$ instead of $\rho(p,k)$.

Using the above equation and the transformation of variables $z = \xi_{\alpha,\nu}e^{\frac{y}{2}}$ (so $dy = \frac{2}{z}dz$), we compute
\begin{align*}
	\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \, dy 
    &= \frac{1}{k!} \int_0^\infty \left(\xi_{\alpha,\nu} e^{\frac{y}{2}}\right)^k 
    	e^{-\xi_{\alpha,\nu} e^{\frac{y}{2}}} \alpha e^{-\alpha y} \, dy\\
    &= \frac{\alpha (\xi_{\alpha,\nu})^{2\alpha}}{\Gamma(k+1)} \int_0^\infty 
    	\left(\xi_{\alpha,\nu} e^{\frac{y}{2}}\right)^{k - 2\alpha} e^{-\xi_{\alpha,\nu} e^{\frac{y}{2}}}
        \, dy\\
    &= \frac{2\alpha (\xi_{\alpha,\nu})^{2\alpha}}{\Gamma(k+1)} \int_{\xi_{\alpha,\nu}}^{\infty} 
    	z^{k -2\alpha-1} e^{-z} \, dz\\
    &=2\alpha (\xi_{\alpha,\nu})^{2\alpha} \frac{\Gamma^+(k - 2\alpha, \xi_{\alpha,\nu})}{\Gamma(k+1)},
\end{align*}
where we recall that $\Gamma$ denotes the Gamma-function and $\Gamma^{+}$ the incomplete Gamma-function.
We therefore conclude that
\begin{equation}\label{eq:degree_distribution_P}
	\Prob{D_\Pcal = k} = 2\alpha (\xi_{\alpha,\nu})^{2\alpha} \frac{\Gamma^+(k - 2\alpha, \xi_{\alpha,\nu})}{\Gamma(k+1)}
\end{equation}

Since $\Gamma^{+}(k-2\alpha, \xi_{\alpha,\nu})/\Gamma(k - 2\alpha) \sim k^{-(2\alpha+1)}$ as $k \to \infty$ \PvdH{@All: Does anyone have a good standard reference for this?} we deduce that
\begin{equation}\label{eq:degree_distribution_P_asymptotics}
	\Prob{D_\Pcal = k} \sim 2\alpha (\xi_{\alpha,\nu})^{2\alpha} k^{-(2\alpha + 1)}
	\quad \text{as } k \to \infty.
\end{equation}

By a similar computation we have the following result, which will be useful later on. For any $\beta > 0$, as $k \to \infty$
\begin{equation}\label{eq:general_integral_rho_y_k}
	\int_0^\infty e^{\beta y} \rho_y(k) \alpha e^{-\alpha y} \, dy
    \sim 2\alpha \left(\xi_{\alpha,\nu}\right)^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
\end{equation}

\subsection{Asymptotic behavior of $c_\infty(k)$}\label{ssec:asymptotics_local_clustering_P}

%\begin{lemma}\label{lem:expectation_clustering_P}
%Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then
%\[
%	\Exp{c_{\Pcal}^\ast(k)} = \frac{\int_0^{\infty} \Delta_{\Pcal}(y) \, 
%	\rho_{y}(k) e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k) 
%	e^{-\alpha y} \, dy}.
%\]
%\end{lemma}
%
%\begin{proof}
%By the Palm-Mecke formula, we have
%\begin{align*}
%	\Exp{c_{\Pcal}^\ast(k)} &= \frac{1}{\Exp{N_\Pcal(k)}}
%		\int_0^{\infty} \int_{-\infty}^{\infty} \Exp{\frac{\ind{D_{\Pcal}(p) = k}}{\binom{k}{2}} \sum_{(p_1, p_2) \in \Pcal} T(p,p_1,p_2)} f_{\alpha,\nu}(x,y) \, dx \, dy\\
%	&= \frac{1}{\Exp{N_\Pcal(k)}} \int_0^{\infty} \int_{-\infty}^{\infty} \binom{k}{2}^{-1}
%		\Delta_{\Pcal}(p,k)\CProb{D_\Pcal(p) = k}{p} f_{\alpha,\nu}(x,y) \, dx \, dy.
%\end{align*}
%Conditioned on the Poisson process $\Pcal$ having $k$ points in $B(p)$, the points are independent random variables $Z_{1}, \dots, Z_{k}$ with probability  distribution $\eta_{p} = \frac{\mu|_{B(p)}}{\mu(B(p))}$. Therefore we have
%\[
%	\Delta_{\Pcal}(p,k) = \binom{k}{2} T_\Pcal(p),
%\]
%and hence, since the entire expression inside the integral does not depend on $x$,
%\begin{align*}
%	\Exp{c_{\Gamma, n}^\ast(k)} 
%	&= \frac{1}{\Exp{N_\Pcal(k)}} \int_0^{\infty} \Delta_{\Pcal}(y) \rho_{\mu, y}(k) e^{-\alpha y} \, dy.
%\end{align*}
%Finally, we note that
%\begin{align*}
%	\Exp{N_\Pcal(k)} &= \Exp{\sum_{p \in \Pcal} \ind{D_\Pcal(p) = k}}
%	= \int_0^{\infty}\int_{-\infty}^\infty \rho_{\mu, p}(k) f_{\alpha,\nu}(x,y) \, dx \, dy
%	= \int_0^{\infty} \rho_{\mu, y}(k) e^{-\alpha y} \, dy
%\end{align*}
%which completes the proof.
%\end{proof}

Recall that
\[
	c_\infty(k) = \frac{\int_0^\infty \rho(y,k) \Delta_\Pcal(y) \alpha e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}.
\]
The asymptotic behavior for the denominator follows from~\eqref{eq:degree_distribution_P_asymptotics}. Hence, the main term to consider is the numerator
\[
	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \, \rho(y,k) \alpha e^{-\alpha y} \, dy,
\]
and in particular the function $\Delta_\Pcal(y)$. The following result establishes the asymptotic behavior of the latter.

\begin{proposition}[Asymptotic behavior of $\Delta_\Pcal(y)$]\label{prop:asymptotics_Delta_y_P}
Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $C_\alpha$ as defined in \eqref{eq:def_C_alpha}. Then there are three, eventually decreasing, functions $\varphi_i : \R_+ \mapsto \R$, $i = 1,2,3$, satisfying
\[
	\lim_{y \to \infty} \varphi_i(y) = 0, 
\]
such that 
\begin{enumerate}
\item for $\frac{1}{2} < \alpha < \frac{3}{4}$,
\[
	\Delta_{\Pcal}(y) = e^{-\frac{y}{2}(4\alpha - 2)} C_\alpha (1 + \varphi_1(y)),
\]
\item for $\alpha = \frac{3}{4}$,
\[
	\Delta_\Pcal(y) = \log\left(\frac{y}{2}\right)e^{-\frac{y}{2}}(1 + \varphi_2(y)),
\]
\item and for $\alpha > \frac{3}{4}$,
\[
	\Delta_{\Pcal}(y) = e^{-\frac{y}{2}} \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}} (1 + \varphi_3(y)).
\]
\end{enumerate}
\end{proposition}

The proof of this proposition is involved and technical. We therefore postpone it till Section \ref{ssec:asymptotics_Delta_y_P} and first use it to prove Theorem \ref{thm:asymptotics_average_clustering_P}.

\begin{proof}[Proof of Theorem \ref{thm:asymptotics_average_clustering_P}]

We only give the proof for the case $\frac{1}{2} < \alpha < \frac{3}{4}$. The proofs for the other two cases are similar. Let $\varphi_1(y)$ be defined as in Proposition \ref{prop:asymptotics_Delta_y_P} and define
\[
	\epsilon_1(k) = \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y
\]
Then we have that
\[
	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
	= C_\alpha \int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y + \epsilon_1(k).
\]

Using \eqref{eq:general_integral_rho_y_k} with $\beta = 2\alpha - 1$ yields,
\begin{equation}\label{eq:asymptotics_clustering_integral}
	\int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y 
	\sim 2\alpha \xi_{\alpha,\nu}^{6\alpha - 2} k^{-(6\alpha - 1)},
\end{equation}
as $k \to \infty$. Therefore, by applying the asymptotic scaling for the denominator~\eqref{eq:degree_distribution_P_asymptotics} we get
\begin{align*}
	c_\infty(k) &= \frac{\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho(y,k) \alpha  e^{-\alpha y} \dd y}
		{\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y} \\
	&\sim C_\alpha 2\alpha \xi_{\alpha,\nu}^{4\alpha - 2} \frac{k^{-(6\alpha - 1)}}{k^{-(2\alpha - 1)}}
	+ \frac{\epsilon_1(k)}{2\alpha \xi_{\alpha,\nu}^{2\alpha} k^{-(2\alpha - 1)}}\\
	&= C_\alpha 2\alpha \xi_{\alpha,\nu}^{4\alpha - 2} k^{-4\alpha + 2} 
    + \frac{1}{2\alpha}\xi_{\alpha,\nu}^{-2\alpha} k^{2\alpha - 1}\epsilon_1(k).
\end{align*}
Hence, to prove the result it is enough to show that
\[
	\lim_{k \to \infty} k^{6\alpha - 3}\epsilon_1(k) = 0.
\]
For this we fix $0 < \varphi < 1$, define $a(k) = 2\log((1-\varphi)k)$ and split the integral into two pieces
\begin{align*}
	\epsilon_1(k) &= \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
	&= \int_0^{a(k)} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
	&\hspace{10pt}+ \int_{a(k)}^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
    	\rho(y,k) \alpha e^{-\alpha y} \dd y.
\end{align*} 
For the first integral we use that $\rho(y,k)$ is increasing on $[0,a(k)]$ and
\[
	k^{6\alpha - 3}\rho(a(k),k) = O\left(\frac{k^{6\alpha - 3 + (1-\varphi)k}}{k!} e^{-(1-\varphi)k}\right) = o(1),
\]
to obtain
\begin{align*}
	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_0^{a_n} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
    	\rho(y,k) \alpha e^{-\alpha y} \dd y\\
	&\le \lim_{n \to \infty} \left(\max_{0 \le y \le a(k)} \varphi_1(y)\right) k^{6\alpha - 1} 
    	\rho(a(k), k) \int_0^\infty \alpha e^{-\alpha y} \dd y = 0.
\end{align*}
For the second integral we first note that due to \eqref{eq:asymptotics_clustering_integral}
\[
	\int_0^\infty e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y = \bigT{k^{-(6\alpha - 1)}}.
\] 
Therefore, using that $\varphi_1(y)$ is eventually decreasing and $\lim_{k \to \infty} \varphi_1(a(k)) = 0$, we obtain
\begin{align*}
	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_{a(k)}^{\infty} \varphi_1(y) 
    	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
	&\le \lim_{k \to \infty} \varphi_1(a(k)) k^{6\alpha - 3} \int_0^\infty 
    	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y = 0,
\end{align*}
which finishes the proof.
\end{proof}

\subsection{Analyzing $\Delta_\Pcal(y)$, an overview.}\label{ssec:asymptotics_Delta_y_P}

We derive the following complete asymptotic expansion of $\Delta_{\Pcal}(y)$, from which then the leading terms can be extracted. The following result proves Proposition \ref{prop:asymptotics_Delta_y_P}, resp. implies it as a corollary after extracting the leading terms.
\begin{proposition}\label{prop:full_expression_delta_P}
\begin{enumerate}
	\item If $\alpha \not = 1$, then
	\begin{align*}
	 \Delta_{\Pcal}(y) &=-\frac{1}{8 (\alpha - 1) \alpha} + \frac{(\alpha - 1/2) e^{-\frac{1}{2}y}}{\alpha - 1} - \frac{(\alpha - 1/2)^2 e^{-y}}{
		4 (\alpha - 1)^2} \\
	&+ 
	(e^{-\frac{1}{2}y})^{4\alpha -2} \left(\frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha (\alpha - 1)^2} + \frac{(\alpha - 
		1/2 ) B^-(1/2; 1 + 2 \alpha, 
		-2 + 2 \alpha)}{2(\alpha - 1) \alpha} \right) \\
	&+ \frac{(1 - 
		e^{-\frac{1}{2}y})^{2 \alpha}}{8 (\alpha - 1) \alpha} - \frac{  
		(e^{-\frac{1}{2}y})^{4 \alpha - 2} B^-(1 - e^{-\frac{1}{2}y}; 2 \alpha, 3 - 4 \alpha)}{4 (\alpha - 1)}
	\end{align*}
	\item If $\alpha = 1$, then
	\begin{align*}
	&\Delta_{\Pcal}(y) =\frac{9}{4} e^{-\frac{1}{2}y} + \frac{1 - 4 e^{-\frac{1}{2}y} + 3 e^{-y}}{4}\ln(1 - e^{-\frac{1}{2}y}) - \frac{7+\pi^2}{8}
e^{-y}  + 
\frac{1}{2}e^{-y}\Li_2(e^{-y})
	\end{align*}
	where $\Li_2(z)=\int_0^z \frac{\ln(1-t)}{t}dt$ is the dipolylogarithm function.
\end{enumerate}
\end{proposition}

%We note that $\Delta_{\Pcal}(y_0)$ is the probability that $(x_1,y_1), (x_2,y_2)$ are neighbours, given that they are neighbours of $(0,y_0)$. (Here we think of $y_0$ as being fixed during the chance experiment and $(x_1,y_1), (x_2,y_2)$ chosen randomly.)

%The computation can be outlined as follows: First of all, we apply a change of variable $z_i = e^{-y_i/2}$, $i=0,1,2$. Then we find an expression for $P(y_0(z_0),y_1(z_1),y_2(z_2))$ depending on several cases in the input variables. The two innermost integrals, which we are going to denote by $P(y_0)$, are computed by partitioning the integration domain into four corresponding subdomains.

To derive this result, recall (see~\eqref{eq:def_delta_p}) that $\Delta_{\Pcal}(y)$ is the probability that $Z_1 \in \BallPo{Z_2}$, where $Z_1, Z_2$ are two independent random variables on $\BallPo{0,y}$ with density 
\[
	\eta_{y}(y^\prime,x^\prime) = \frac{f_{\alpha,\nu}(x^\prime, y^\prime)\ind{(x^\prime, y^\prime \in B_{\Pcal}(0,y)}}{\mu(B_{\Pcal}(0,y))}.
\]

For notational convenience we will switch to using $y_0$ instead of $y$. Note that the random variables $Z_i = (x_i,y_i)$, for $i = 1,2$, correspond to first sampling $y_i$ according to the density
\[
	g(y_i) := \left(\alpha -\frac{1}{2}\right) e^{-(\alpha-\frac{1}{2})y_i}
\] 
and then sampling $x_i$ uniformly in $[-e^{\frac{1}{2}(y+y_i)},e^{\frac{1}{2}(y+y_i)}]$. With this in mind we define $P(y_0,y_1,y_2)$ to be the probability that $(0,y_0), (x_1,y_1), (x_2,y_2)$ form a triangle where $x_1$ and $x_2$ are uniform random variables in, respectively, $[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$ and  $[-e^{\frac{1}{2}(y_0+y_2)},e^{\frac{1}{2}(y_0+y_2)}]$.

>>>>

\section{Clustering and the degree of the typical point in $\Ginf$\label{sec:Ginf}\label{sec:asymptotics_average_clustering_ast_P}}

As mentioned earlier, we plan to make use of the Campbell-Mecke formula for comparing the clustering coefficient and function of $\GPo$ with certain quantities associated with $\Ginf$. We will be considering the Poisson process $\Pcal$ to which we add one additinal point $(0,y)$ on the $y$-axis. In some computations the height $y$ will be fixed, but eventually we shall take it exponentially distributed with parameter $\alpha$, and independent of $\Pcal$.
We refer to $(0,y)$ as ``the typical point''.

To provide some intu\"{\i}tion for this definition and name, note that we can alternatively view $\Pcal$ as follows. 
We take a constant intensity Poisson process on $\eR$ corresponding to the $x$-coordinates, and to each point
we attach a random ``mark'', corresponding to the $y$-coordinate, where the marks are i.i.d.~exponentially distributed with parameter $\alpha$.

Since $c(G)$ is defined as an average over all vertices of the graph, it is not immediately obvious how to meaningfully define a corresponding notion for infinite graphs, and similarly for the clustering function, the degree sequence, etc.
We can however without any issues speak of the (expected) clustering coefficient of the typical point, or the expected clustering coefficient given that it has degree k, or the distribution of the degree of the typical point. (All considered in the graph obtained from $\Ginf$ by adding the typical point to its vertex set.)

If $p = (x,y) \in \eR\times[0,\infty)$ is a point, not necessarily part of the Poisson process, then we will write

$$ \mu(y) = \mu(p) := \mu(\BallPo{p}). $$
Integrating the intensity function of $\Pcal$ over $\BallPo{p}$ gives

$$ \begin{array}{rcl} 
\mu(y) & = & \int_{\BallPo{p}} f(x',y') \, dx' \,d y'  
 = \int_0^\infty \int_{-e^{(y+y')/2}}^{e^{(y+y')/2}} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dx' \, dy' \\
& = & \int_0^\infty 2 e^{(y+y')/2} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dy' 
 = \frac{2\alpha \nu e^{y/2}}{\pi} \int_0^\infty e^{(\frac12-\alpha)y'} \, dy' \\
& = & \frac{2\alpha \nu e^{y/2}}{\pi(\alpha-\frac12)} = \xi e^{y/2}.
\end{array} $$

\subsection{The degree of the typical point\label{ssec:degrees_infinite_model}}

Before considering clustering we briefly investigate the distribution of the degree of 
the typical point. 
For $p = (x,y) \in \eR\times[0,\infty)$ we define
\begin{equation}
	\rho(p,k) := \Prob{\Po(\mu(y)) = k},
\end{equation}

where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$. 
We will often write $\rho(y,k)$ instead of $\rho(p,k)$.

Let the random variable $D$ denote the degree of the typical point.
Since the typical point has a height that is independent of the Poisson process and exponential($\alpha$)-distributed:
\begin{equation}\label{eq:def_pk}
	p_k := \Pee( D=k ) = \int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \, dy.
\end{equation}

Using the transformation of variables $z = \xi e^{\frac{y}{2}}$ (so $dy = \frac{2}{z}dz$), we compute
\begin{align*}
	p_k
    &= \frac{1}{k!} \int_0^\infty \left(\xi e^{\frac{y}{2}}\right)^k 
    	e^{-\xi e^{\frac{y}{2}}} \alpha e^{-\alpha y} \, dy\\
    &= \frac{\alpha \xi^{2\alpha}}{k!} \int_0^\infty 
    	\left(\xi e^{\frac{y}{2}}\right)^{k - 2\alpha} e^{-\xi e^{\frac{y}{2}}}
        \, dy\\
    &= \frac{2\alpha \xi^{2\alpha}}{k!} \int_{\xi}^{\infty} 
    	z^{k -2\alpha-1} e^{-z} \, dz\\
    &= \frac{2\alpha \xi^{2\alpha}\Gamma^+(k - 2\alpha, \xi)}{k!},
\end{align*}
where we recall that $\Gamma$ denotes the Gamma-function and $\Gamma^{+}$ the upper incomplete Gamma-function.
Note that, unsurprisingly, this is identical to the expression Gugelmann et al.~\cite{gugelmann2012random} gave for the limiting degree distribution of $G(n;\alpha,\nu)$. Using Stirling's approximation to the gamma function, we find that

\begin{equation}\label{eq:degree_distribution_P_asymptotics}
	p_k \sim 2\alpha\xi^{2\alpha} k^{-(2\alpha + 1)}
	\quad \text{as } k \to \infty.
\end{equation}

By a similar computation we have the following result, which will be useful later on. For any $\beta > 0$, as $k \to \infty$
\begin{equation}\label{eq:general_integral_rho_y_k}
	\int_0^\infty e^{\beta y} \rho(y, k) \alpha e^{-\alpha y} \, dy
    \sim 2\alpha \xi^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
\end{equation}

\subsection{The expected clustering coefficient and function of the typical point}

Let the random variable $C$ denote the clustering coefficient of the typical point $(0,y)$, in the graph obtained from $\Ginf$ by adding $(0,y)$. We {\em define}
\[
	\gamma := \Ee C, \quad \gamma(k) := \Ee\left( C | D = k \right).
\]
(Where we take the expection over both the Poisson point process $\Pcal$ and $y \isd \text{exp}(\alpha)$, independent of the Poisson process $\Pcal$.) We shall show shortly that these take on the values stated in Theorem~\ref{thm:maincc} and~\ref{thm:mainkfixed}.

For any fixed value $y_0>0$, the set of points inside $\BallPo{(0,y_0)}$ is a Poisson process with intensity $f \cdot 1_{\BallPo{(0,y_0)}}$. As $\mu(\BallPo{(0,y_0)}) = \mu(y_0) = \xi e^{y_0/2} < \infty$, this can be described alternatively by the experiment where we first pick $N \isd \Po( \mu(y_0) )$ then and we take $N$ i.i.d.~points in $\BallPo{(0,y_0)}$ according to the probability density $f \cdot 1_{\BallPo{(0,y_0)}} / \mu(y_0)$. (That is, the intesity function of the Poisson point process, but set to zero outside of $\BallPo{(0,y_0)}$ and renormalized in such a way that it integrates to one.) Hence, if we condition on the event that $y$ takes on some fixed value $y_0$ and that there are exactly $k$ points of $\Pcal$ inside $\BallPo{(0,y_0)}$, then those $k$ points behave like $k$ i.i.d.~points in $\BallPo{(0,y_0)}$ chosen according to the mentioned renormalized probability density function. This shows that, for every $k\geq 2$:
\[
	\Ee\left( C | D=k, y=y_0 \right) 
	= \frac{1}{{k\choose 2}} \Ee\left( \sum_{1\leq i < j \leq k} 1_{\{u_i\in \BallPo{u_j}\}} \right)
	= \Exp{1_{\{u_1\in\BallPo{u_2}\}}},
\]
where $u_1,\dots, u_n$ are i.i.d.~points in $\BallPo{(0,y_0)}$ with the above mentioned density.
Note that this does not depend on the value of $k$. For notational convenience, we'll write 
\[ 
	P(y_0) := \Exp{1_{\{u_1\in\BallPo{u_2}\}}},
\]
with $u_1, u_2$ as above.

We now observe that 
\[
	\gamma(k) = \Ee( C | D=k ) = \int_0^\infty \Ee\left( C | D=k, y=y_0 \right) g_k(y_0) \, d y_0,
\]
where $g_k$ denotes the density of $y$ {\em conditional on} $D=k$. That is,
\[
	g_k(y_0)  = \frac{\rho(y_0, k) \alpha e^{-\alpha y_0} }{\int_0^\infty \rho(t, k) \alpha e^{-\alpha t} \, d t}
	= \frac{1}{p_k} \cdot \rho(y_0, k) \alpha e^{-\alpha y_0}.
\]
Hence, 
\begin{equation}\label{eq:gammakint}
\gamma(k) 
= \frac{1}{p_k} \cdot \int_0^\infty P(y_0) \rho(y_0,k) \alpha e^{-\alpha y_0} \, d y_0. 
\end{equation}
This also gives
\begin{equation}\label{eq:gammaint}
\begin{array}{rcl} 
\gamma 
& = & \displaystyle \Ee C = \sum_{k\geq 2} \Ee( C | D=k )\Pee( D=k ) \\
& = & \displaystyle \int_0^\infty P(y_0) \left( \sum_{k=2}^\infty \rho(y_0,k) \right) \alpha e^{-\alpha y_0} \, d y_0 \\
& = & \displaystyle \int_0^\infty P(y_0) \left(1 - \rho(y_0,0)-\rho(y_0,1)\right) \alpha e^{-\alpha y_0} \, d y_0.
\end{array}
\end{equation}

A key step is to derive the following explicit expression for $P(y)$.

\begin{lemma}\label{lem:Paneq1}
%\begin{enumerate}
%	\item 
	If $\alpha \not = 1$, then
	\begin{align*}
	 P(y) &=-\frac{1}{8 (\alpha - 1) \alpha} + \frac{(\alpha - 1/2) e^{-\frac{1}{2}y}}{\alpha - 1} - \frac{(\alpha - 1/2)^2 e^{-y}}{
		4 (\alpha - 1)^2} \\
	&+ 
	(e^{-\frac{1}{2}y})^{4\alpha -2} \left(\frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha (\alpha - 1)^2} + \frac{(\alpha - 
		1/2 ) B^-(1/2; 1 + 2 \alpha, 
		-2 + 2 \alpha)}{2(\alpha - 1) \alpha} \right) \\
	&+ \frac{(1 - 
		e^{-\frac{1}{2}y})^{2 \alpha}}{8 (\alpha - 1) \alpha} - \frac{  
		(e^{-\frac{1}{2}y})^{4 \alpha - 2} B^-(1 - e^{-\frac{1}{2}y}; 2 \alpha, 3 - 4 \alpha)}{4 (\alpha - 1)}
	\end{align*}
% 	\item If $\alpha = 1$, then
% 	\begin{align*}
% 	&P(y) =\frac{9}{4} e^{-\frac{1}{2}y} + \frac{1 - 4 e^{-\frac{1}{2}y} + 3 e^{-y}}{4}\ln(1 - e^{-\frac{1}{2}y}) - \frac{7+\pi^2}{8}
% e^{-y}  + 
% \frac{1}{2}e^{-y}\Li_2(e^{-y})
% 	\end{align*}
% 	where $\Li_2(z)=\int_0^z \frac{\ln(1-t)}{t}dt$ is the dipolylogarithm function.
%\end{enumerate}
\end{lemma}

We will prove this lemma in a sequence of steps.

Recall that $P(y_0)$ is the probability that $u_1 = (x_1,y_1), u_2 = (x_2,y_2)$ are neighbours in $\Ginf$, where
$u_1, u_2$ are i.i.d.~with probability density $f \cdot 1_{\BallPo{(0,y_0)}} / \mu(y_0)$.
In particular

$$ \begin{array}{rcl} 
\Pee( y_i > t ) 
& = & 
\frac{\nu\alpha}{\pi \mu(y_0)} \int_t^\infty \int_{-e^{(s+y_0)/2}}^{e^{(s+y_0)/2}} e^{-\alpha s}\, d s \\
& = & 
\frac{\nu\alpha}{\pi \mu(y_0)} \int_t^\infty 2 e^{(s+y_0)/2} \cdot e^{-\alpha s}\, d s \\
& = & 
\frac{2 \nu\alpha e^{y_0/2} }{\pi \xi e^{y_0/2} (\alpha-\frac12) }  \cdot e^{(\frac12-\alpha)t} \\
& = & 
 e^{(\frac12-\alpha)t},
\end{array} $$

\noindent
using that $\mu(y_0) = \xi e^{y_0/2} = \left(\frac{2\alpha\nu}{\pi(\alpha-\frac12)}\right) e^{y_0/2}$.
Thus, $y_1, y_2$ are exponentially distributed with parameter $\alpha-\frac12$.
Now note that, for each $t>0$, the probability density $f \cdot 1_{\BallPo{(0,y_0)}} / \mu(y_0)$
is constant on $[-e^{(t+y_0)/2}, e^{(t+y_0)/2}] \times \{t\}$ and it is 
vanishes on $(-\infty, -e^{(t+y_0)/2}) \times \{t\} \cup (e^{(t+y_0)/2},\infty)\times\{t\}$.

Hence, given the height $y_i$ of $u_i$, the $x$-coordinate of $u_i$ is uniform in $[-e^{\frac{1}{2}(y+y_i)},e^{\frac{1}{2}(y+y_i)}]$. 
With this in mind we define $P(y_0,y_1,y_2)$ to be the probability that $(0,y_0), (x_1,y_1), (x_2,y_2)$ 
satisfy $|x_1-x_2| \leq e^{(y_1+y_2)/2}$, where $x_1$ and $x_2$ are independent uniform random variables in, respectively, 
$[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$ and  $[-e^{\frac{1}{2}(y_0+y_2)},e^{\frac{1}{2}(y_0+y_2)}]$.
We have that

\begin{align}\label{eq:delta_P}
 P(y_0) = (\alpha-1/2)^2 \int_0^\infty \int_0^\infty P(y_0, y_1, y_2) e^{-(\alpha-1/2)(y_1+y_2)} 
 \dd y_2 \dd y_1.
\end{align}

\subsubsection{Determining $P(y_0,y_1,y_2)$}

To compute the integral~\eqref{eq:delta_P} it will be convenient to use the 
change of variable $z_i = e^{-y_i/2}$, for $i= 0, 1, 2$. 
We will write $y_i(z_i)$ to stress the dependence between $y_i$ and $z_i$. 
The following result completely characterizes $P(y_0,y_1,y_2)$.
